---
output:
  pdf_document: default
  html_document: default
---

```yaml
---
title: "ASSIGNMENT 2.1_AmericanCommunitySurvey"
author: "Bhushan Suryawanshi"
date: '2020-06-10'
output:
  html_document: default
---
```
This is your second exercise with real data. This time, instead of a bank of test scores, we will use the 2014 American Community Survey. These data are maintained by the US Census Bureau and are designed to show how communities are changing.

Through asking questions of a sample of the population, it produces national data on more than 35 categories of information, such as education, income, housing, and employment.

For this assignment, you will need to load and activate the ggplot2 package. (I urge you to do the DataCamp exercise first!). For this deliverable, you should provide the following:

1. What are the elements in your data (including the categories and data types)?

```{r}
      acs_df <- read.csv("acs-14-1yr-s0201.csv", stringsAsFactors = FALSE)
      head(acs_df)
      sapply(acs_df, class)
```

Answer - Head shows the sample data in the data set. The function sapply helps to get
datatype of the column. In this dataset we have 8 columns out of which 5 are columns are numerical data, 
And 3 are categorical data. 

2. Please provide the output from the following functions: str(); nrow(); ncol()
```{r}
      str(acs_df)
      nrow(acs_df)
      ncol(acs_df)
      
```

Answer - Above function str also helps to get column details of the dataset.
The function nrow() and ncol() gives number of rows and number of columns in dataset respectively.

3. Create a Histogram of the HSDegree variable using the ggplot2 package.

a. Set a bin size for the Histogram.

b. Include a Title and appropriate X/Y axis labels on your Histogram Plot.

```{r}
      library(ggplot2)
      bw = 5
      n_obs = sum(!is.na(acs_df$HSDegree))
      ggplot(acs_df, aes(HSDegree)) + geom_histogram(bins=10) + ggtitle('HSDegree vs. Count') + xlab('HSDegree') + ylab('Count') + stat_function(fun = function(x) dnorm(x, mean = mean(acs_df$HSDegree), sd = sd(acs_df$HSDegree)) * bw * n_obs  )
      
```


4. Answer the following questions based on the Histogram produced:

a. Based on what you see in this histogram, is the data distribution unimodal?

b. Is it approximately symmetrical?

c. Is it approximately bell-shaped?

d. Is it approximately normal?

e. If not normal, is the distribution skewed? If so, in which direction?

f. Include a normal curve to the Histogram that you plotted.

g. Explain whether a normal distribution can accurately be used as a model for this data.

Answer - A unimodal distribution is a distribution with one clear peak or most frequent value.
Based on the above histogram we can see that the data shown is unimodel but not normally distributed. 
It is negatively skewed distribution. 

5. Create a Probability Plot of the HSDegree variable.

```{r}
    ggplot(acs_df, aes(HSDegree)) +  geom_density()
```

6. Answer the following questions based on the Probability Plot:


```{r}
   summary(acs_df$HSDegree)
```
a. Based on what you see in this probability plot, is the distribution approximately normal? Explain how you know.

Answer - Based on probability distribution we can say the distribution is approximately normal because
more than 60% of the data is near the mean of the distribution. Also we can observe data between 1st and 3rd quartile
it is approximately more than 60%. 

b. If not normal, is the distribution skewed? If so, in which direction? Explain how you know.

Answer - The data is not exactly normal but negatively skewed because mean is less than median. 
In normal distribution difference between mean and median is 0. 

7. Now that you have looked at this data visually for normality, you will now quantify normality with numbers using the stat.desc() function. Include a screen capture of the results produced.

```{r}
  library(pastecs)
  stat.desc(acs_df)
  
  library(e1071)  
  skewness(acs_df$HSDegree)
  kurtosis(acs_df$HSDegree)
  
  library(sqldf)
  a <- sqldf("SELECT DISTINCT id FROM acs_df  ORDER BY RANDOM(*) LIMIT 5")
  small_acs_df = sqldf("SELECT * FROM acs_df WHERE id IN a")
  small_acs_df
  skewness(small_acs_df$HSDegree)
  kurtosis(small_acs_df$HSDegree)
```

8. In several sentences provide an explanation of the result produced for skew, kurtosis, and z-scores. In addition, explain how a change in the sample size may change your explanation?

Answer - Skewness talks about lack of symmetry in the data. Where as kurtosis talks about pointiness at the end, 
The sample size or size of data does affect the distribution. As shown in the above example we picked random 5 data 
points from the give sample. Then we calculated skewness and kurtosis for current sample size of 136 observations. We see that if we use 
all data then the skewness is -1.67 where as for smaller sample it shows -0.79. Same is the case with kurtosis, with 
all data we get kurtosis 4.35 and with small sample it is -1.22, Which means sample size does affect the analysis. 
Getting right sample size is key to data analysis. In our example if we increase sample size we may get normal curve and we have higher
probability of having more population with HSDegree. 
